Thermal relaxation is important in convective simulations: \\ on the time evolution of flows and how to avoid unnecessary thermal rundown

### 2020-02-20 tex/mixedft_evolution_ms.tex
corrects fig 3 caption

\subsection{Evolved Structure}
\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_1D_profiles.pdf}
\caption{ 
	(left three panels) Shown are the time- and horizontally-averaged temperature (top), temperature in upflows and downflows (middle), and fluxes (bottom) for a TT-to-FT (orange) and TT (purple) case at Ra$_{\Delta T} = 10^{10}$.
	The boundary layer regions are separated from the bulk by thin vertical lines.
	The boundary layers are examined in more detail in the right six panels: the middle column examines the bottom boundary layers, and the right panel examines the top boundary layers.
	The insets show the \% difference between the FT and TT solutions.
	There are appreciable (a few \%) differences in two places: the enthalpy flux (likely due to a short sampling window), and in the mean temperature profiles in upflows and downflows at the bottom (fixed flux) boundary.	
\label{fig:rbc_1D_profiles} }
\end{figure}

>>>>

\subsection{Evolved Structure}
\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_1D_profiles.pdf}
\caption{ 
	[NOTE: This is currently data from Ra$_{\Delta T} = 10^8$; $10^9$ is converging a bit further on Pleiades]
	(left three panels) Shown are the time- and horizontally-averaged temperature (top), temperature in upflows and downflows (middle), and fluxes (bottom) for an FT (orange) and TT (purple) case at Ra$_{\Delta T} = 10^{9}$.
	The boundary layer regions are separated from the bulk by thin vertical lines.
	The boundary layers are examined in more detail in the right six panels: the middle column examines the bottom boundary layers, and the right panel examines the top boundary layers.
	The insets show the \% difference between the FT and TT solutions.
	There are appreciable (a few \%) differences in two places: the enthalpy flux (likely due to a short sampling window), and in the mean temperature profiles in upflows and downflows at the bottom (fixed flux) boundary.	
\label{fig:rbc_1D_profiles} }
\end{figure}
